Sparse Function-space Representation \\ of Neural Networks

### 2023-05-23 paper/main.tex
rl updates

\textbf{Laplace-GGN}
In the Laplace-GGN experiments we use the Laplace library from \cite{daxberger2021laplace}
with the full hessian structure over all of the network's weights.
We then use the GLM predictions.
As expected, the Laplace-GGN is also able to solve the sparse reward environment.

\textbf{Ensemble}
The ensemble experiments used $5$ members where each member was an MLP with two hidden layers of width $128$ and Tanh activations, \ie\ the same architecture as the other experiments.
At each episode, the ensemble was trained for $10000$ iterations using the Adam optimiser.
We used a learning rate $0.0001$ and a batch size of $64$.
At each time step in the planning horizon we used the following procedure to sample from the ensemble.
First, the mean and variance of the ensemble members predictions were calculated.
Next, we sampled from the resulting Gaussian.
\cref{fig:rl} shows that the ensemble required more environment interaction to solve the task.
This is indicated by the green line not converging within the $50$ episodes shown in the figure.

>>>>

\textbf{Laplace-GGN}
In the Laplace-GGN experiments we used the Laplace library from \cite{daxberger2021laplace}
with the full hessian structure over all of the network's weights.
We then used the GLM predictions.
As expected, the Laplace-GGN is also able to solve the sparse reward environment.

\textbf{Ensemble}
The ensemble experiments used $5$ members where each member was an MLP with one hidden layer of width $128$ and Tanh activations, \ie\ the same architecture as the other experiments.
At each episode, the ensemble was trained for $10000$ iterations using the Adam optimiser.
We used a learning rate $0.0001$ and a batch size of $64$.
At each time step in the planning horizon we used the following procedure to sample from the ensemble.
First, the mean and variance of the ensemble members predictions were calculated.
Next, we sampled from the resulting Gaussian.
\cref{fig:rl} shows that the ensemble required more environment interaction to solve the task.
This is indicated by the green line not converging within the $50$ episodes shown in the figure.
